---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pokemon

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

`pokemon` is an R package that contains Pokémon-related datasets. The first Pokémon video game came out in 1996, and Nintendo has since released nine generations of games, including 37 individual games in the main series. It is the second best-selling video game series of all time and is actively played by millions of people. The Pokédex is an encyclopedic collection of stats for all Pokémon in the game series. Previously, only Pokédex data could be found, but this package expands the availability of data by including data sets related to items and moves, as well as the Pokédex. Our data is retrieved from PokéAPI (https://pokeapi.co), a public database of Pokémon-related data that uses URL links as a programming interface. The goal of this package is to create a design that allows users to view and easily interact with extensive Pokémon-related data without needing to collect it themselves, because no such package currently exists (to our knowledge). This package can help create visualizations to compare different types of Pokémon, demonstrating evolution charts, examining the prevalence of particular attack or defense moves, and more. It allows Pokémon enthusiasts and those hunting for datasets to perform Pokémon-related data analysis more smoothly.

Note limitations: This data does not account for the two most recent Pokémon game releases: Pokémon Shining Pearl and Brilliant Diamond, and Pokémon Legends: Arceus, nor will it incorporate data from Pokémon Scarlet and Violet (to be released Fall 2022). Some Pokémon Sword and Shield data may be inaccurate due to communication errors from the API. Some information from the API has not been added or updated.


## Installation

You can install the development version of pokemon from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
devtools::install_github("abbidabbers/pokemon")
```


## Load

```{r}
library(pokemon)
```

## Available Tables

- `pokedex`: Detailed organizer for data included in the official Pokédex such as order, name, types, species, height, weight, abilities, base experience, stats, and held items for each Pokémon. 
- `items`: A more in-depth set of metadata about items in the Pokémon games, such as item ID, name, cost, category, the power and effect of the move "Fling" when used with this item, and the Pokémon that can hold it.
- `moves`: A collection of data about moves in the Pokémon games, including name, accuracy, power, generation, etc.


## Example: Pokédex

```{r example}
head(pokemon::pokedex)
```

## Contributors

- [Abbie Benfield](https://github.com/abbidabbers)
- [Kacey Jean-Jacques](https://github.com/kaceyjj)
- [Elina Gordon-Halpern](https://github.com/egordonhalpern)

## Acknowledgements

Many thanks to the folks at PokeAPI for their amazing work
