---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pokemon

<!-- badges: start -->
<!-- badges: end -->

`pokemon` is an R package that contains Pokémon-related datasets. The first Pokémon video game came out in 1996, and Nintendo has since released nine generations of games, including 37 individual games in the main series. It is the second best-selling video game series of all time and is actively played by millions of people. Previously, only Pokédex data could be found, but this package expands the availability by including datasets related to regions and moves, as well as the Pokédex. The goal of this package is to create a design that allows users to view and easily interact with extensive Pokémon-related data without needing to collect it themselves because no such package currently exists (to our knowledge). This package can help create visualizations to compare different types of Pokémon, demonstrating evolution charts, examining the prevalence of particular attack or defense moves, and more. It allows Pokémon enthusiasts and those hunting for datasets to perform Pokémon-related data analysis more smoothly.


## Installation

You can install the development version of pokemon from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
devtools::install_github("abbidabbers/pokemon")
```


## Load

```{r}
library(pokemon)
```

## Available Tables

- `pokedex`: a small subset of the Pokédex
  - Note: type defense is based on the primary ability if one of the abilities affects type defense
- more will be coming


## Example: Pokédex

```{r example}
head(pokemon::pokedex)
```

## Contributors

- [Abbie Benfield](https://github.com/abbidabbers)
- [Kacey Jean-Jacques](https://github.com/kaceyjj)
- [Elina Gordon-Halpern](https://github.com/egordonhalpern)
