---
title: "pokemon_vignette"
authors: "Abbie Benfield, Elina Gordon-Halpern, Kasey Jean-Jacques"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pokemon_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pokemon)
library(dplyr)
```

## About `pokemon`
`pokemon` is a package that contains datasets and analysis functionality for Pokémon, a Nintendo classic and the second-best selling video game of all time.

Our data is pulled from PokéAPI (https://pokeapi.co), a public database with massive amounts of Pokémon-related information stored in JSON files. Many of these files are heavily nested and difficult to interact with, so our package allows users to easily import and interact with the API data in R.

## Inspiration

## About the Datasets 
We have wrangled and cleaned data for three main tables: `pokedex`, `item_index`, and `moves_index`.
`pokedex` is our largest available table, detailing the name, type, species, height, weight, abilities, stats, and items for every Pokémon. Type, ability, and stats columns include nested metadata about each of these variables.
`item_index` is a more in depth collection of meta data about the items in the `pokedex`. This table organizes the id, name, cost, and category of each item, as well as the Pokémon that can hold it and the power and effect of using the move "fling" with that item (Fling is a combat move).
`moves_index` is a detailed set of information about all Pokémon moves, organizing them by name, generation, accuracy, power, damage class, and the Pokémon that can use them.

## Who should use this Package?

## What can we do with this Data?

## Functionality and Examples

# Example 1:

Below is a demonstration of a potential use for the item index table. We have used a simple data visualization to analyze a potential relationship between an item's fling power and its cost.

```{r}
library(dplyr)
library(ggplot2)

head(pokemon::item_index)
ggplot(data = item_index, mapping = aes(x = fling_power, y = item_cost)) + 
  geom_jitter() + 
  ylim(0, 20000) +
  labs(title = "Item Cost by Fling Power", x = "Fling Power", y = "Item Cost" )

```

**Note: The y limits for this visualization have been reduced for reading clarity, but the items table does include high outliers, with the highest item cost being 100,000 (monetary units for the Pokémon games are not specified).

## Notes and Limitations
his data does not account for the two most recent Pokémon game releases, Pokémon Shining Pearl and Brilliant Diamond, and Pokémon Legends: Arceus, because the API has not yet added it to their database. It also does not incorporate data from the upcoming games, Pokémon Scarlet and Violet (scheduled for release in Fall 2022). According to the PokéAPI's documentation, some  Sword and Shield data may be inaccurate because of the method they used to obtain the information. Additionally, some information from the API has not been added or updated. For this package, we intentionally selected variables that have data for all generations.
